Generate Networks

### 2015-09-08 code/01_generate_networks.Rmd
save networks as an igraph object

>>>>

## Save networks for later use

```{r}
networks <- plyr::dlply(ntw, "Site", function(x){
	edg <- x %>% 
		dplyr::select(-Site)
	ver <- edg %>%
		dplyr::select(-weight) %>%
		tidyr::gather(type, name, pla, pol) %>%
		dplyr::distinct() %>%
		dplyr::select(name, type)

	igraph::graph_from_data_frame(edg, directed = F, vertices = ver)
})

saveRDS(networks, "./data/bartomeus/networks.dat", ascii = TRUE, compress = FALSE)
```
